Analysis of the 2005--2015 Earthquake Sequence in Northern Iran Using the Visibility Graph Method

### 2016-08-20 results.tex
finished new  figure 9

% \begin{figure*}[t]
% 	\centering
% 	\includegraphics[scale=0.4]{figures/pdf/Figure10.pdf} 
% 	\caption{ Variation of $k-M$ slope  and $b-value$ (Left), and $ < T_c >$ (Right) as a function of time for three tectonic seismic regions in north Iran. Black arrows show the occurrence of the major earthquakes. Numbers on arrows indicate the moment magnitude of the earthquake (see Fig.~\ref{fig:mag-time} for reference).  The magnitude-time series are presented as a filled plot blew each plot. The variation of the heigh of filled plots are corresponding to the event magnitudes. Decreasing the value of  $<T_c>$  ,  $k-M$ , and  $b-value$  before large earthquakes predominantly happened in all tectonic seismic regions.}
% 	\label{fig:tc}
% \end{figure*}

>>>>

\begin{figure*}[t]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-09} 
	\caption{ Variation of $k-M$ slope  and $b-value$ (Left), and $ < T_c >$ (Right) as a function of time for three tectonic seismic regions in north Iran. Black arrows show the occurrence of the major earthquakes. Numbers on arrows indicate the moment magnitude of the earthquake (see Fig.~\ref{fig:mag-time} for reference).  The magnitude-time series are presented as a filled plot blew each plot. The variation of the heigh of filled plots are corresponding to the event magnitudes. Decreasing the value of  $<T_c>$  ,  $k-M$ , and  $b-value$  before large earthquakes predominantly happened in all tectonic seismic regions.}
	\label{fig:tc}
\end{figure*}
